Strong coupling between scales in a multi-scalar model of urban dynamics

### 2021-01-31 Docs/Papers/Multiscale/paper/paper_old.tex
arxiv

\begin{thebibliography}{}

\bibitem[Banos et~al., 2015]{banos2015importance}
Banos, A., Corson, N., Gaudou, B., Laperri{\`e}re, V., and Coyrehourcq, S.~R.
  (2015).
\newblock The importance of being hybrid for spatial epidemic models: a
  multi-scale approach.
\newblock {\em Systems}, 3(4):309--329.

\bibitem[Batty, 2005]{batty2005agents}
Batty, M. (2005).
\newblock Agents, cells, and cities: new representational models for simulating
  multiscale urban dynamics.
\newblock {\em Environment and Planning A}, 37(8):1373--1394.

\bibitem[Batty, 2018]{batty2018inventing}
Batty, M. (2018).
\newblock {\em Inventing future cities}.
\newblock MIT press.

\bibitem[Bedau, 2002]{bedau2002downward}
Bedau, M. (2002).
\newblock Downward causation and the autonomy of weak emergence.
\newblock {\em Principia: an international journal of epistemology},
  6(1):5--50.

\bibitem[Belem and M{\"u}ller, 2013]{belem2013organizational}
Belem, M. and M{\"u}ller, J.~P. (2013).
\newblock An organizational model for multi-scale and multi-formalism
  simulation: Application in carbon dynamics simulation in west-african
  savanna.
\newblock {\em Simulation Modelling Practice and Theory}, 32:83--98.

\bibitem[Boulet et~al., 2020]{boulet2020coupling}
Boulet, X., Zargayouna, M., Scemama, G., and Leurent, F. (2020).
\newblock Coupling multi-agent and macroscopic simulators of traffic.
\newblock In {\em Agents and Multi-agent Systems: Technologies and Applications
  2019}, pages 323--332. Springer.

\bibitem[Chavalarias et~al., 2009]{chavalarias2009french}
Chavalarias, D., Bourgine, P., Perrier, E., Amblard, F., Arlabosse, F., Auger,
  P., Baillon, J.-B., Barreteau, O., Baudot, P., Bouchaud, E., et~al. (2009).
\newblock French roadmap for complex systems 2008-2009.

\bibitem[Cheng and Masser, 2003]{cheng2003modelling}
Cheng, J. and Masser, I. (2003).
\newblock Modelling urban growth patterns: a multiscale perspective.
\newblock {\em Environment and Planning A}, 35(4):679--704.

\bibitem[Clarke et~al., 2007]{clarke2007decade}
Clarke, K.~C., Gazulis, N., Dietzel, C., and Goldstein, N.~C. (2007).
\newblock A decade of sleuthing: Lessons learned from applications of a
  cellular automaton land use change model.
\newblock {\em Classics in IJGIS: twenty years of the international journal of
  geographical information science and systems}, pages 413--427.

\bibitem[Crociani et~al., 2016]{crociani2016multi}
Crociani, L., L{\"a}mmel, G., and Vizzari, G. (2016).
\newblock Multi-scale simulation for crowd management: a case study in an urban
  scenario.
\newblock In {\em International Conference on Autonomous Agents and Multiagent
  Systems}, pages 147--162. Springer.

\bibitem[Favaro and Pumain, 2011]{favaro2011gibrat}
Favaro, J.-M. and Pumain, D. (2011).
\newblock Gibrat revisited: An urban growth model incorporating spatial
  interaction and innovation cycles.
\newblock {\em Geographical Analysis}, 43(3):261--286.

\bibitem[Ford et~al., 2019]{ford2019multi}
Ford, A., Barr, S., Dawson, R., Virgo, J., Batty, M., and Hall, J. (2019).
\newblock A multi-scale urban integrated assessment framework for climate
  change studies: A flooding application.
\newblock {\em Computers, Environment and Urban Systems}, 75:229--243.

\bibitem[Gabaix, 1999]{gabaix1999zipf}
Gabaix, X. (1999).
\newblock Zipf's law for cities: an explanation.
\newblock {\em Quarterly journal of Economics}, pages 739--767.

\bibitem[Hjorth et~al., 2020]{hjorth2020levelspace}
Hjorth, A., Head, B., Brady, C., Wilensky, U., et~al. (2020).
\newblock Levelspace: A netlogo extension for multi-level agent-based modeling.
\newblock {\em Journal of Artificial Societies and Social Simulation},
  23(1):1--4.

\bibitem[James et~al., 2018]{james2018zipf}
James, C., Azaele, S., Maritan, A., and Simini, F. (2018).
\newblock Zipf's and taylor's laws.
\newblock {\em Physical Review E}, 98(3):032408.

\bibitem[Joy and Vogel, 2015]{joy2015toronto}
Joy, M. and Vogel, R.~K. (2015).
\newblock Toronto’s governance crisis: A global city under pressure.
\newblock {\em Cities}, 49:35--52.

\bibitem[Liao and Gaudin, 2017]{liao2017ouverture}
Liao, L. and Gaudin, J.-P. (2017).
\newblock L’ouverture au march{\'e} en chine (ann{\'e}es 1980-2000) et le
  d{\'e}veloppement {\'e}conomique local: une forme de gouvernance
  multi-niveaux?
\newblock {\em Cybergeo: European Journal of Geography}.

\bibitem[Murcio et~al., 2015]{murcio2015urban}
Murcio, R., Morphet, R., Gershenson, C., and Batty, M. (2015).
\newblock Urban transfer entropy across scales.
\newblock {\em PLoS One}, 10(7):e0133780.

\bibitem[Pumain, 1997]{pumain1997pour}
Pumain, D. (1997).
\newblock Pour une th{\'e}orie {\'e}volutive des villes.
\newblock {\em Espace g{\'e}ographique}, 26(2):119--134.

\bibitem[Pumain and Reuillon, 2017]{pumain2017urban}
Pumain, D. and Reuillon, R. (2017).
\newblock {\em Urban Dynamics and Simulation Models}.
\newblock Springer International.

\bibitem[Raimbault, 2018]{raimbault2018calibration}
Raimbault, J. (2018).
\newblock Calibration of a density-based model of urban morphogenesis.
\newblock {\em PloS one}, 13(9):e0203516.

\bibitem[Raimbault, 2019a]{raimbault:halshs-02265423}
Raimbault, J. (2019a).
\newblock {Evolving accessibility landscapes: mutations of transportation
  networks in China}.
\newblock In Aveline-Dubach, N., editor, {\em {PATHWAYS OF SUSTAINABLE URBAN
  DEVELOPMENT ACROSS CHINA: THE CASES OF HANGZHOU, DATONG AND ZHUHAI}}, pages
  89--108. {Imago Editor}.
\newblock ebook.

\bibitem[Raimbault, 2019b]{raimbault:halshs-02284933}
Raimbault, J. (2019b).
\newblock {Towards integrated urban models for sustainable policies}.
\newblock In {\em {Urban analytics at the interface between environment, human
  health and behaviour}}, Shanghai, China. {Tongji University and The Alan
  Turing Institute}.

\bibitem[Raimbault, 2019c]{raimbault:halshs-02013006}
Raimbault, J. (2019c).
\newblock {Towards multi-scalar models for the co-evolution of transportation
  networks and territories}.
\newblock In {\em {Theo Quant 2019}}, Besan{\c c}on, France. {Universit{\'e} de
  Franche-Comt{\'e}}.

\bibitem[Raimbault, 2020a]{raimbault2020comparison}
Raimbault, J. (2020a).
\newblock A comparison of simple models for urban morphogenesis.
\newblock {\em arXiv preprint arXiv:2008.13277}.

\bibitem[Raimbault, 2020b]{raimbault2020hierarchy}
Raimbault, J. (2020b).
\newblock Hierarchy and co-evolution processes in urban systems.
\newblock {\em arXiv preprint arXiv:2001.11989}.

\bibitem[Raimbault, 2020c]{raimbault2020indirect}
Raimbault, J. (2020c).
\newblock Indirect evidence of network effects in a system of cities.
\newblock {\em Environment and Planning B: Urban Analytics and City Science},
  47(1):138--155.

\bibitem[Raimbault, 2020d]{raimbault2020unveiling}
Raimbault, J. (2020d).
\newblock Unveiling co-evolutionary patterns in systems of cities: a systematic
  exploration of the simpopnet model.
\newblock In {\em Theories and Models of Urbanization}, pages 261--278.
  Springer.

\bibitem[Raimbault et~al., 2020]{raimbault2020scala}
Raimbault, J., Perret, J., and Reuillon, R. (2020).
\newblock A scala library for spatial sensitivity analysis.
\newblock {\em arXiv preprint arXiv:2007.10667}.

\bibitem[Reuillon et~al., 2013]{reuillon2013openmole}
Reuillon, R., Leclaire, M., and Rey-Coyrehourcq, S. (2013).
\newblock Openmole, a workflow engine specifically tailored for the distributed
  exploration of simulation models.
\newblock {\em Future Generation Computer Systems}, 29(8):1981--1990.

\bibitem[Rozenblat and Pumain, 2018]{Rozenblat2018}
Rozenblat, C. and Pumain, D. (2018).
\newblock {\em Toward a Methodology for Multi-scalar Urban System Policies},
  pages 385--393.
\newblock Springer Singapore, Singapore.

\bibitem[Shu et~al., 2020]{shu2020modelling}
Shu, B., Zhu, S., Qu, Y., Zhang, H., Li, X., and Carsjens, G.~J. (2020).
\newblock Modelling multi-regional urban growth with multilevel logistic
  cellular automata.
\newblock {\em Computers, Environment and Urban Systems}, 80:101457.

\bibitem[Torrens and O'Sullivan, 2001]{torrens2001cellular}
Torrens, P.~M. and O'Sullivan, D. (2001).
\newblock Cellular automata and urban simulation: where do we go from here?

\bibitem[Wegener and F{\"u}rst, 2004]{wegener2004land}
Wegener, M. and F{\"u}rst, F. (2004).
\newblock Land-use transport interaction: state of the art.
\newblock {\em Available at SSRN 1434678}.

\bibitem[Wegener and Spiekermann, 2018]{wegener2018multi}
Wegener, M. and Spiekermann, K. (2018).
\newblock Multi-level urban models: Integration across space, time and
  policies.

\bibitem[White, 2006]{white2006modeling}
White, R. (2006).
\newblock Modeling multi-scale processes in a cellular automata framework.
\newblock In {\em Complex artificial environments}, pages 165--177. Springer.

\bibitem[Xu and Gao, 2019]{xu2019directional}
Xu, T. and Gao, J. (2019).
\newblock Directional multi-scale analysis and simulation of urban expansion in
  auckland, new zealand using logistic cellular automata.
\newblock {\em Computers, Environment and Urban Systems}, 78:101390.

\bibitem[Xu et~al., 2020]{xu2020urban}
Xu, T., Gao, J., Coco, G., and Wang, S. (2020).
\newblock Urban expansion in auckland, new zealand: a gis simulation via an
  intelligent self-adapting multiscale agent-based model.
\newblock {\em International Journal of Geographical Information Science},
  34(11):2136--2159.

\bibitem[Yu et~al., 2018]{yu2018modeling}
Yu, Y., He, J., Tang, W., and Li, C. (2018).
\newblock Modeling urban collaborative growth dynamics using a multiscale
  simulation model for the wuhan urban agglomeration area, china.
\newblock {\em ISPRS International Journal of Geo-Information}, 7(5):176.

\bibitem[Zhu and Tian, 2020]{zhu2020dynamic}
Zhu, J. and Tian, S. (2020).
\newblock A dynamic urban lake area evolution model based on multilevel grid,
  cellular automata, and multiagent system.
\newblock {\em Complexity}, 2020.

\end{thebibliography}

>>>>

\bibliographystyle{apalike}
\bibliography{biblio}
